### 2024-03-04 src/paper.tex
Minor fixes

\begin{tcolorbox}[title={Konstrukcija}]
\begin{equation*}
  \begin{aligned}
    \Pos\Char{a} &\MoveX{\Char{a}} \Char{a}\Pos\\
    %(\RE{R})\Pos &\MoveX{\Char{a}} \RE{R}\\
    \Pos\Char{a} &\MoveX{\Char{b}} \Char{a}\text{, kjer } \Char{a} \neq \Char{b}
  \end{aligned}
\end{equation*}
\end{tcolorbox}

@@

    \draw (t0.north east) edge[->, shorten <>=-2pt+\pgflinewidth] node[auto]{$\{\Char{a}\}$} (t1.south west);
    \draw (t0) edge[->] node[auto]{$\{\Char{b}\}$} (t2);
    \draw (t0.south east) edge[->, shorten <>=-2pt+\pgflinewidth] node[auto]{$\{\Char{c}, \Char{d}\}$} (t3.north west);
  \end{tikzpicture}
\end{center}

@@

\begin{center}
  \begin{tikzpicture}
    \tikzset{
      node distance=1cm,
      every state/.style={rectangle, rounded corners, inner sep=0.5em},
      initial text=$ $,
      shorten <>/.style={shorten >=#1, shorten <=#1},
    }
    \node[state, initial, accepting, label=above left:$\Automaton{\RE{r}}$, label={above right:=}] (u0) {$\Kleene{(\Pos\Char{a} \Spc \Char{a} \Union \Pos\Char{b})}$};
    \node[state, initial, right=of u0] (u1) {$\Kleene{(\Char{a} \Pos \Char{a} \Union \Char{b})}$};
    \node[state, right=of u1, accepting, label={above right:=}] (u2) {$\Kleene{(\Pos \Char{a} \Spc \Char{a} \Union \Char{b})}\Pos$};
    \node[state, accepting, below=of u1, label={above right:=}] (u3) {$\Kleene{(\Pos\Char{a} \Spc \Char{a} \Union \Char{b})}\Pos$};
    \draw (u0) edge[->] node[auto]{$\Char{a}$} (u1);
    \draw (u1) edge[->] node[auto]{$\Char{a}$} (u2);
    \draw (u0) edge[->] node[auto]{$\Char{b}$} (u3.west);

    \node[state, initial, accepting, below=3 of u0, label=above left:$\Automaton{\RE{r}}$] (p0) {$\Kleene{(\Pos\Char{a} \Spc \Char{a} \Union \Pos\Char{b})}$};
    \node[state, right=of p0] (p1) {$\Kleene{(\Char{a} \Pos \Char{a} \Union \Char{b})}$};
    \draw (p0.north east) edge[->, bend left, shorten <>=-2pt+\pgflinewidth] node[auto]{$\Char{a}$} (p1.north west);
    \draw (p1.south west) edge[->, bend left, shorten <>=-2pt+\pgflinewidth] node[auto]{$\Char{a}$} (p0.south east);
    \draw (p0) edge[->, loop below] node[auto]{$\Char{b}$} (p0);
  \end{tikzpicture}
\end{center}

>>>>

\begin{tcolorbox}[title={Konstrukcija}]
\begin{equation*}
  \begin{aligned}
    \Pos\Char{a} &\MoveX{\Char{a}} \Char{a}\Pos\\
    (\RE{R})\Pos &\MoveX{\Char{a}} \RE{R}\\
    \Pos\Char{a} &\MoveX{\Char{b}} \Char{a}\text{, kjer } \Char{a} \neq \Char{b}
  \end{aligned}
\end{equation*}
\end{tcolorbox}

@@

    \draw (t0.north east) edge[->, shorten <>=-2pt+\pgflinewidth] node[auto]{$\{\Char{a}\}$} (t1.south west);
    \draw (t0) edge[->] node[auto]{$\{\Char{b}\}$} (t2);
    \draw (t0.south east) edge[->, shorten <>=-2pt+\pgflinewidth] node[auto]{$\{\Char{c}, \Char{d}\}$} (t3.north west);
  \end{tikzpicture}
\end{center}
Paziti moramo, da avtomat ne postane nedeterminističen.

@@

\begin{center}
  \begin{tikzpicture}
    \tikzset{
      node distance=1cm,
      every state/.style={rectangle, rounded corners, inner sep=0.5em},
      initial text=$ $,
      shorten <>/.style={shorten >=#1, shorten <=#1},
    }
    \node[state, initial, accepting, label=above left:$\Automaton{\RE{r}}$, label={above right:=}] (u0) {$\Kleene{(\Pos\Char{a} \Spc \Char{a} \Union \Pos\Char{b})}\Pos$};
    \node[state, initial, right=of u0] (u1) {$\Kleene{(\Char{a} \Pos \Char{a} \Union \Char{b})}$};
    \node[state, right=of u1, accepting, label={above right:=}] (u2) {$\Kleene{(\Pos \Char{a} \Spc \Char{a} \Union \Pos\Char{b})}\Pos$};
    \node[state, accepting, below=of u1, label={above right:=}] (u3) {$\Kleene{(\Pos\Char{a} \Spc \Char{a} \Union \Pos\Char{b})}\Pos$};
    \draw (u0) edge[->] node[auto]{$\Char{a}$} (u1);
    \draw (u1) edge[->] node[auto]{$\Char{a}$} (u2);
    \draw (u0) edge[->] node[auto]{$\Char{b}$} (u3.west);

    \node[state, initial, accepting, below=3 of u0, label=above left:$\Automaton{\RE{r}}$] (p0) {$\Kleene{(\Pos\Char{a} \Spc \Char{a} \Union \Pos\Char{b})}\Pos$};
    \node[state, right=of p0] (p1) {$\Kleene{(\Char{a} \Pos \Char{a} \Union \Char{b})}$};
    \draw (p0.north east) edge[->, bend left, shorten <>=-2pt+\pgflinewidth] node[auto]{$\Char{a}$} (p1.north west);
    \draw (p1.south west) edge[->, bend left, shorten <>=-2pt+\pgflinewidth] node[auto]{$\Char{a}$} (p0.south east);
    \draw (p0) edge[->, loop below] node[auto]{$\Char{b}$} (p0);
  \end{tikzpicture}
\end{center}
